---
title: "NSDC ML"
author: "Khang Thai"
date: "2024-05-20"
output: html_document
---

```{r}
library("tidyverse")
library("caret")
library("randomForest")

data <- read.csv("host.csv")
```

```{r}
data <- data %>%
  select(host_is_superhost, host_response_rate, host_acceptance_rate, host_has_profile_pic, host_identity_verified, ratings, days_since_host, host_response_time_within_an_hour) %>%
  na.omit()

data$host_is_superhost <- as.factor(data$host_is_superhost)

set.seed(123)
trainIndex <- createDataPartition(data$host_is_superhost, p = 0.7, list = FALSE, times = 1)

data_train <- data[trainIndex, ]
data_test <- data[-trainIndex, ]

model <- randomForest(host_is_superhost ~ ., data = data_train)

```

```{r}
predictions <- predict(model, data_test)
confusionMatrix(predictions, data_test$host_is_superhost)
```
Accuracy: 76.51%
Sensitivity: 64.42% superhost correctly identified
Specificity: 86.19% non-superhost correctly identified
Balanced Accuracy: 75.30% 


```{r}
plot(model)

importance(model)

varImpPlot(model)
```
Rating shows most important variable when identifying a host becoming a superhost.


Suggestions:
1. Prioritize maintaining high ratings across different aspects
2. Maintain high host_response_rate and host_acceptance_rate to show responsiveness and reliability.
3. Have a profile picture to enhance trustworthiness.
4. Get identity verified by Airbnb to increase credibility.
5. Respond to guest inquiries within an hour to provide excellent customer service.




```{r}
param_grid <- expand.grid(
  mtry = c(2, 3, 4, 5),
  nodesize = c(1, 5, 10)
)


set.seed(123)
tuned_model <- train(
  host_is_superhost ~ .,
  data = data_train,
  method = "rf",
  trControl = trainControl(method = "cv", number = 5),
  tuneGrid = param_grid
)

best_param <- tuned_model$bestTune

final_model <- randomForest(
  host_is_superhost ~ .,
  data = data_train,
  mtry = best_params$mtry,
  nodesize = best_params$nodesize
)

predictions_tuned <- predict(final_model, data_test)
confusionMatrix(predictions_tuned, data_test$host_is_superhost)

varImpPlot(final_model)
```

